Music Perception 2: Preregistered Analysis

### 2022-03-14 experiment-1/analysis/analysis.Rmd
update analysis for first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@

@@

@@

# KOT
- articulation and teaching judgement
- linear regression lines and 95% confidence interval (gray)

@@

@@

@@

## Forte (***)
```{r, echo = FALSE}
# normality check
vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
vel_for_norm_performance <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)

@@

@@

>>>>

### Remove outliers for dynamics (outside 2SD)
```{r, echo = FALSE}
mean = mean(ioi[Skill == "dynamics"]$Mean)
sd = sd(ioi[Skill == "dynamics"]$Mean)

# normality check
shapiro.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

@@

### Remove outliers for dynamics (outside 2SD)
```{r, echo = FALSE}
mean = mean(ioi_tra[Skill == "dynamics"]$Mean)
sd = sd(ioi_tra[Skill == "dynamics"]$Mean)

# normality check
shapiro.test(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

@@

### Remove outliers for articulation (outside 2SD)
```{r, echo = FALSE}
mean = mean(cv[Skill == "articulation"]$CV)
sd = sd(cv[Skill == "articulation"]$CV)

# normality check
shapiro.test(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
shapiro.test(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)

qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)

qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)

cor.test(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching, cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
```

@@

### Remove outliers for dynamics (outside 2SD)
```{r, echo = FALSE}
mean = mean(cv[Skill == "dynamics"]$CV)
sd = sd(cv[Skill == "dynamics"]$CV)

# normality check
shapiro.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
shapiro.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)

qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)

qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)

cor.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching, cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
```
# KOT
- articulation and teaching judgement
- linear regression lines and 95% confidence interval (gray)

@@

### Remove outliers for forte (outside 2SD)
```{r, echo = FALSE}
mean = mean(kot_all[Subcomponent == "Forte"]$Mean)
sd = sd(kot_all[Subcomponent == "Forte"]$Mean)

# normality check
shapiro.test(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

@@

### Remove outliers for piano (outside 2SD)
```{r, echo = FALSE}
mean = mean(kot_all[Subcomponent == "Piano"]$Mean)
sd = sd(kot_all[Subcomponent == "Piano"]$Mean)

# normality check
shapiro.test(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

@@

## Forte (**)
```{r, echo = FALSE}
# normality check
vel_for_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Forte"]$Teaching)
vel_for_norm_performance <- shapiro.test(vel_all[Subcomponent == "Forte"]$Mean)

@@

### Remove outliers for legato (outside 2SD)
```{r, echo = FALSE}
mean = mean(vel_all[Subcomponent == "Legato"]$Mean)
sd = sd(vel_all[Subcomponent == "Legato"]$Mean)

# normality check
shapiro.test(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

@@

### Remove outliers for ltos (outside 2SD)
```{r, echo = FALSE}
mean = mean(vel_diff_all[Subcomponent == "LtoS"]$Mean)
sd = sd(vel_diff_all[Subcomponent == "LtoS"]$Mean)

# normality check
shapiro.test(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

### 2022-03-14 experiment-1/analysis/prereg_analysis/prereg_analysis.Rmd
update analysis for first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Design

- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques separately. The order of the blocks was counterbalanced across participants.
- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented within a block.

@@

```{r packages, include = FALSE}
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# midi
if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
# stats
if (!require("afex")) {install.packages("afex"); require("afex")}
```

@@

t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
```

@@

```{r plot2, echo = FALSE}
ind_data_ad <- data[subjectNumber != 4, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
ind_data_ad <- ind_data_ad[order(subjectNumber, Skill)]

@@

t.test(ind_data_ad[Skill == "articulation"]$Percent, mu = 50, alternative = "two.sided")
```

@@

t.test(ind_data_ad[Skill == "dynamics"]$Percent, mu = 50, alternative = "two.sided")
```

@@

t.test(ind_data_ad[Skill == "articulation"]$Percent, ind_data_ad[Skill == "dynamics"]$Percent, paired = TRUE)
```

>>>>

## Design
- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques separately. The order of the blocks was counterbalanced across participants.
- 48 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented within a block.

@@

```{r packages, include = FALSE}
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# midi
if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
# plot
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
# stats
if (!require("afex")) {install.packages("afex"); require("afex")}
if (!require("rstatix")) {install.packages("rstatix"); require("rstatix")}
```

@@

ttest_all <- t.test(ind_data$Percent, mu = 50, alternative = "two.sided")
ttest_all
```

### Effect size
```{r, echo = FALSE}
coheneff_all <- ind_data %>% cohens_d(Percent ~ 1, mu = 50)
coheneff_all
```

@@

```{r plot2, echo = FALSE}
ind_data_ad <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Skill)]
ind_data_ad <- ind_data_ad[order(subjectNumber, Skill)]

@@

ttest_art <- t.test(ind_data_ad[Skill == "articulation"]$Percent, mu = 50, alternative = "two.sided")
ttest_art
```

### Effect size
```{r, echo = FALSE}
coheneff_art <- ind_data_ad[Skill == "articulation"] %>% cohens_d(Percent ~ 1, mu = 50)
coheneff_art
```

@@

ttest_dyn <- t.test(ind_data_ad[Skill == "dynamics"]$Percent, mu = 50, alternative = "two.sided")
ttest_dyn
```

### Effect size
```{r, echo = FALSE}
coheneff_dyn <- ind_data_ad[Skill == "dynamics"] %>% cohens_d(Percent ~ 1, mu = 50)
coheneff_dyn
```

@@

ttest_paired <- t.test(ind_data_ad[Skill == "articulation"]$Percent, ind_data_ad[Skill == "dynamics"]$Percent, paired = TRUE)
ttest_paired
```
### Effect size
```{r, echo = FALSE}
coheneff_paired <- ind_data_ad %>% cohens_d(Percent ~ Skill, mu = 50)
coheneff_paired
```

### 2022-03-14 experiment-2/analysis/analysis.Rmd
update analysis for first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Dynamics (n.s.)
```{r, echo = FALSE}
# normality check
ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)

@@

## Dynamics (*)
```{r, echo = FALSE}
# normality check
ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
ioi_dyn_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)

@@

@@

## Piano (*)
```{r, echo = FALSE}
# normality check
vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
vel_pia_norm_performance <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)

@@

cor_vel_pia_spearman <- cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
cor_vel_pia_spearman
```
## Legato (n.s.)
```{r, echo = FALSE}
# normality check
vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
vel_leg_norm_performance <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)

@@

@@

cor_vel_diff_ptof_spearman <- cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean, method = "spearman", exact = FALSE)
cor_vel_diff_ptof_spearman
```
## Legato to Staccato (n.s.)
```{r, echo = FALSE}
# normality check
vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
vel_diff_ltos_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)

>>>>

## Dynamics (*)
```{r, echo = FALSE}
# normality check
ioi_dyn_norm_teaching <- shapiro.test(ioi[Skill == "dynamics"]$Teaching)
ioi_dyn_norm_performance <- shapiro.test(ioi[Skill == "dynamics"]$Mean)

@@

## Dynamics (**)
```{r, echo = FALSE}
# normality check
ioi_dyn_tra_norm_teaching <- shapiro.test(ioi_tra[Skill == "dynamics"]$Teaching)
ioi_dyn_tra_norm_performance <- shapiro.test(ioi_tra[Skill == "dynamics"]$Mean)

@@

### Remove outliers for dynamics (outside 2SD)
```{r, echo = FALSE}
mean = mean(cv[Skill == "dynamics"]$CV)
sd = sd(cv[Skill == "dynamics"]$CV)

# normality check
shapiro.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
shapiro.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)

qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)

qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)

cor.test(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching, cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
```

@@

### Remove outliers for forte (outside 2SD)
```{r, echo = FALSE}
mean = mean(vel_all[Subcomponent == "Forte"]$Mean)
sd = sd(vel_all[Subcomponent == "Forte"]$Mean)

# normality check
shapiro.test(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

## Piano (**)
```{r, echo = FALSE}
# normality check
vel_pia_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Piano"]$Teaching)
vel_pia_norm_performance <- shapiro.test(vel_all[Subcomponent == "Piano"]$Mean)

@@

cor_vel_pia_spearman <- cor.test(vel_all[Subcomponent == "Piano"]$Teaching, vel_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
cor_vel_pia_spearman
```

### Remove outliers for forte (outside 2SD)
```{r, echo = FALSE}
mean = mean(vel_all[Subcomponent == "Piano"]$Mean)
sd = sd(vel_all[Subcomponent == "Piano"]$Mean)

# normality check
shapiro.test(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

## Legato (n.s.)
```{r, echo = FALSE}
# normality check
vel_leg_norm_teaching <- shapiro.test(vel_all[Subcomponent == "Legato"]$Teaching)
vel_leg_norm_performance <- shapiro.test(vel_all[Subcomponent == "Legato"]$Mean)

@@

### Remove outliers for ftop (outside 2SD)
```{r, echo = FALSE}
mean = mean(vel_diff_all[Subcomponent == "FtoP"]$Mean)
sd = sd(vel_diff_all[Subcomponent == "FtoP"]$Mean)

# normality check
shapiro.test(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

@@

cor_vel_diff_ptof_spearman <- cor.test(vel_diff_all[Subcomponent == "PtoF"]$Teaching, vel_diff_all[Subcomponent == "PtoF"]$Mean, method = "spearman", exact = FALSE)
cor_vel_diff_ptof_spearman
```

### Remove outliers for ltop (outside 2SD)
```{r, echo = FALSE}
mean = mean(vel_diff_all[Subcomponent == "PtoF"]$Mean)
sd = sd(vel_diff_all[Subcomponent == "PtoF"]$Mean)

# normality check
shapiro.test(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
shapiro.test(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

cor.test(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching, vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
```

## Legato to Staccato (n.s.)
```{r, echo = FALSE}
# normality check
vel_diff_ltos_norm_teaching <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
vel_diff_ltos_norm_performance <- shapiro.test(vel_diff_all[Subcomponent == "LtoS"]$Mean)

### 2022-03-14 experiment-2/analysis/prereg_analysis/prereg_analysis.Rmd
update analysis for first draft
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Experiment
## Preregistered Analysis
We originally had a analysis plan to look at the accuracy of participants' judgements whether participants would be able to judge stimuli from the teaching condition as "teaching". For more detailed explanations, please see [the OSF preregistration](https://osf.io/z3j69).

## Stimuli
- Stimuli were selected from the previous study ([the sound of teaching music/experiment-2](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2)).
- 36 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 72 stimuli). The half of them was selected from the teaching condition and the other half was from the performing condition.
  + 18 for teaching-articulation performances
  + 18 for performing-articulation performances
  + 18 for teaching-dynamics performances
  + 18 for performing-dynamics performances

## Design

- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques (expressions) separately. The order of the blocks was counterbalanced across participants.
- 36 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented across participants.

>>>>

# Experiment
## Preregistered Analysis
The preregistered analysis aims to investigate whether participants could distinguish performances produced for teaching purposes from those produced for performing purposes. For more detailed explanations, please see [the OSF preregistration](https://osf.io/z3j69).

## Stimuli
- Stimuli were selected from the previous study ([the sound of teaching music/experiment-2](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2)).
- 36 stimuli were randomly chosen from each technique (either articulation or dynamics - therefore in total 72 stimuli). Half of them was selected from the teaching condition and the other half was from the performing condition.
  + 18 for teaching-articulation performances
  + 18 for performing-articulation performances
  + 18 for teaching-dynamics performances
  + 18 for performing-dynamics performances

## Design
- 2 blocks (articulation / dynamics): participants were asked to do the same task for two techniques separately. The order of the blocks was counterbalanced across participants.
- 36 trials for each block (each stimulus was presented only once) and the stimuli were randomly presented within a block.
